\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{multicol}
\usepackage{dirtytalk}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.85in} %Left Margin
\addtolength{\evensidemargin}{11.2in}
\addtolength{\textwidth}{1.6in} % Right Margin
\addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{1.8in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage{titlesec}
\usepackage{xcolor}

\titleformat{\section}
{\vspace{-4pt}\scshape\raggedright\color{black}}
{}{0em}{}
[\color{black}
\vspace{-0.7mm}
\titlerule
\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\usepackage{setspace}

\newcommand{\resumeItem}[1]{
  \item\small{
    \begin{spacing}{0.92}
      #1
    \end{spacing}
    \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4] {
  \vspace{-3pt}
  \item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small#2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.99\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.99\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
  \begin{itemize}[leftmargin=0in, rightmargin=0in, label={}, wide=0pt]
}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{contour}
\usepackage{ulem}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\renewcommand{\underline}[1]{{\color{blue}\uline{#1}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large \scshape Soumya Snigdha Kundu} \\ 

    \small +44-7436-215-187 $|$
    \href{https://www.linkedin.com/in/soumyaskundu/}
    {\myuline{Linkedin}}  $|$
    \href{https://scholar.google.com/citations?user=WmHtKBYAAAAJ&hl=en&oi=ao}
    {\myuline{G-Scholar}} $|$
    \href{https://github.com/aymuos15}
    {\myuline{Github}} $|$
    \href{https://aymuos15.github.io/}
    {\myuline{Website}} $|$
    \href{https://discuss.pytorch.org/u/soumya_kundu/summary}
    {\myuline{PyTorch-Forums}} $|$ \href{https://www.alphaxiv.org/profile/6770c388aa490fa39fe15b19/aymuos}{\myuline{alphaxiv}} $|$
    \href{mailto:soumyawork15@gmail.com} 
    {\myuline{E-mail}} $|$ London, United Kingdom
\end{center}
\vspace{-7.5mm}

%-----------EDUCATION-------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {King's College London | \texttt{Ph.D. Biomedical Engineering and Imaging Science Research}\vspace{-1mm}}
      {Oct. 2023 -- Oct. 2027 {\scriptsize (Expected)}}
      {\textit{\textnormal{\myuline{\texttt{Advisors:}} Prof. Tom Vercauteren {\scriptsize (Computational)} and Dr. Jonathan Shapey {\scriptsize (Clinical)}}}}
      {}
    \vspace{-0.5mm}
    \resumeSubheading
      {\textit{\textnormal{\myuline{\texttt{Thesis:}} \hspace{2mm} Artificial Intelligence-driven Management of Brain Tumours}}}
      {}{}{}
    \vspace{-3.5mm}
        
    \resumeSubheading
      {Queen Mary University of London | \texttt{M.Sc. Machine Learning for Visual Data Analytics {\scriptsize (Distinction)}}\vspace{-1mm}}
      {Sep. 2022 -- Sep. 2023}
      {\textit{\textnormal{\myuline{\texttt{Advisors:}} Prof. Greg Slabaugh {\scriptsize (Computational)} and Mr. Vineet Batta {\scriptsize (Clinical)}}}}
      {}
    \vspace{-0.5mm}
    \resumeSubheading
      {\textit{\textnormal{\myuline{\texttt{Thesis:}} \hspace{2mm} Unveiling the Localization Advantage in Automated Orthopaedic Identification}}}
      {}{}{}
    \vspace{-3.5mm}
    
    \resumeSubheading
      {SRM Institute of Science and Technology | \texttt{B.Tech. Computer Science and Engineering {\scriptsize (Distinction)}}}
      {Jul. 2018 -- May. 2022}
      {}{}
\resumeSubHeadingListEnd
\vspace{-9mm}

\section{Selected Publications}
\small{
\resumeSubHeadingListStart

    \resumeSubheading
        {}{}{}{}
    \vspace{-7mm}
    \resumeItemListStart
          
      \resumeItem{\textbf{S. S. Kundu} et al., \say{Spinal Osteophyte Detection Via Robust Patch Extraction on Minimally Annotated X-Rays}, in \myuline{IEEE International Symposium on Biomedical Imaging} (\textit{\textbf{ISBI}}), 2024.}
      
      \resumeItem{R. Naidu and \textbf{S. S. Kundu}, \say{Improved variants of Score-CAM via Smoothing and Integrating}, in \myuline{Responsible Computer Vision Workshop @ Conference on Computer Vision and Pattern Recognition} (\textit{\textbf{CVPR Workshop}}), 2021. }

      \resumeItem{\textbf{S. S. Kundu}, \say{A Distributed Deep Learning Framework for Federated Big Medical Image Analysis}, in \myuline{IEEE International Conference on Big Data (\textbf{Big Data}), 2021.}}
    \resumeItemListEnd

\resumeSubHeadingListEnd
}

\textbf{Reviewing}: MICCAI, ICML, NeurIPS, ICLR, AISTAS and IEEE-ISBI.


\vspace{-3mm}

\section{Research Experience}
  
\resumeSubHeadingListStart
    \resumeSubheading
        {University of Oxford | Research Intern}
        {\hspace*{-5cm}Prof. Bartek Papiez $|$ Fall 2023}
        {}
        {}
        \vspace{-4mm}
            \resumeItemListStart
                \resumeItem{Developed the \underline{$1^{st}$ spinal new bone formation (osteophytes) identification pipeline} achieving a \underline{200\% increase from baseline precision} scores through a custom multi-view post-processing strategy \textit{SegPatch}. \hfill {\scriptsize[ISBI'24]}}

            \resumeItem{Investigated weighed ensembling for knee radiographic performance evaluation to handle extreme class imbalance.
            \hfill {\scriptsize[MICAD'24]}}
            
            \resumeItemListEnd
\vspace{1.5mm}

    \resumeSubheading
        {TRIUMF-Canada's particle accelerator centre | Research Intern}
        {\hspace*{-5cm} Prof. Akira Konaka \& Dr. Patrick De Perio $|$  Summer 2021}
        {}{}
        \vspace{-4mm}
            \resumeItemListStart
                \resumeItem{Collaborated with engineers and physicists at the \textit{Water Cherenkov Machine Learning Group} to design a robust scaling function to facilitate a 70\% loss decrease for the reconstruction of energy, position and angles of electrons in a \textit{regression} neural network.}
\resumeItemListEnd
\vspace{1.5mm}
          
                \resumeSubheading
        {National Institute of Technology, Durgapur | Research Intern}
        {Prof. Debashis Nandi $|$ Winter 2021}
        {}
        {}
        \vspace{-4mm}
            \resumeItemListStart

            \resumeItem{Engineered a compound classification + segmentation pipeline for segmenting multiple sclerosis lesions that \underline{outperforms stand-alone segmentation networks by 10-12\% dice score.} \hfill {\scriptsize[Computer methods and programs in biomedicine 2022]}}
     
            \resumeItemListEnd
    
\resumeSubHeadingListEnd
\vspace{-4mm}

\section{Industry Experience}
\resumeSubHeadingListStart

    \resumeSubheading
        {TCS Research \& IIIT-Hyderabad | Research Scientist}
        {Mrs. Ramya Hebbalaguppe \& Prof. Ranjitha Prasad $|$ Fall 2024}
        {}
        {}
                \vspace{-4mm}

            \resumeItemListStart
                                
                \resumeItem{Responsible for instituting complete explainablity throughout the NORD-F pipeline by generating class activation maps,  and reporting Out-of-domain specific fairness and calibration metrics.}

                \resumeItem{Devised multiple large-scale ablations to surmount the efficiency of NORD-F and improved the the performance by 5\% through the integration of a ConvNeXt based backbone.}
        
          \resumeItemListEnd

\vspace{1mm}

    \resumeSubheading
        {Stealth Startup | Founding Engineer}
        {Oct. 2020 -- Sept. 2022}
        {}
        {}
        \vspace{-4mm}
            \resumeItemListStart
                
                \resumeItem{Raised $\sim$ \pounds50000 for the \underline{$1^{st}$ end-to-end automated system to identify 10 separate orthopaedic implants in plain radiographs}, while reducing data requirements by $>$90\% and achieving 98\% F1-Score.  \hfill {\scriptsize[ISBI'23, MIUA'23]}}
                
                \resumeItem{Spearheaded a multi-institutional collaboration involving renowned Orthopaedic Surgeons, gathering valuable insights and perspectives to publish an in-depth systematic review of 50+ papers on automated orthopaedic implant identification. \hfill {\scriptsize[SICOT'21, IOACON'22, EFORT'22]}}
                
                \resumeItem{Maintained the internal \textit{HPC} and \textit{MLOps} infrastructure along with reviewing monthly software updates of junior members, identifying potential improvements and increasing code performance metrics by an average of 15\%.}
        
          \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-4mm}

\section{Open-Source Software \& Hackathons/Competitions}
  
\resumeSubHeadingListStart

    \resumeSubheading
        {UltraFlwr: Federated Object Detection}
        {Jun 2024 - March 2025}
        {}{}
        \vspace{-4mm}
            \resumeItemListStart
                \resumeItem{
Developed a library which combines Flower and Ultralytics libraries to perform and benchmark Federated Object Detection.}
                \resumeItem{
Proposed a novel partial aggregration strategy YOLO-PA, specifically to perform partial aggregation in YOLO models. \hfill{\scriptsize[MICCAI'25]}}
    \resumeItemListEnd
    \vspace{2mm}

    \resumeSubheading
        {Insta-Match}
        {Jan 2024 - Oct 2024}
        {}{}
        \vspace{-4mm}
            \resumeItemListStart

\resumeItem{The \underline{$1^{st}$} GPU optimised library to compute \textit{segment matching} based performance metrics for segmentation. \hfill{\scriptsize[SPIE Medical Imaging'25]}}
    \resumeItemListEnd
    \vspace{2mm}

\resumeSubheading
    {GPU Optimised Random Walker and Random Walker with Restart Algorithm}
    {Jan 2024 - March 2023}
    {}{}
    \vspace{-3mm}
        \resumeItemListStart
        \resumeItem{Re-purposed the commonly used random walker repository for speed ups with PyTorch and CUDA.}
\resumeItemListEnd
\vspace{2mm}

\resumeSubheading
    {Promptly-Cited: Citation based Inference via Pseudo-Retrieval-Augmented Generation}
    {Dec 2023}
    {}{}
    \vspace{-3mm}
        \resumeItemListStart
        \resumeItem{Developed test-time citation based LLM inference in small context scenarios. \hfill{\scriptsize[NeurIPS Workshop 25]}}
\resumeItemListEnd
\vspace{2mm}

\resumeSubheading
    {Anthropic London Hackathon}
    {Dec 2023}
    {}{}
    \vspace{-3mm}
        \resumeItemListStart
            \resumeItem{Built a Python debugging agent based a novel prompting scheme which earned the recognition of \underline{Top 8 finalist} in the Hackathon.}
        
        \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-3.5mm}

%-----------PROGRAMMING SKILLS-----------
\section{Programming and Software Development}
\vspace{-1mm}
Python, C++, HTML, CSS, Javascript $|$ PyTorch, JAX, NumPy, OpenCV, Docker, Git, Slurm, Bash, \LaTeX.
\vspace{-3mm}

%-----------Fellowships and Awards------------
\section{Fellowships, Grants and Awards.}
\vspace{-1mm}

MRC DTP Postgraduate \textit{Studentship} \hspace*{2.8mm} --- King's College London $||$ $<$ 2\% Selection rate. $||$ $\sim$ \pounds205000 $||$ 2023 Cohort \\
BDI Summer \textit{Internship} Programme \hspace*{4mm} --- University of Oxford $||$ 1 of 4 selected applicants $||$ 2023 Cohort\\
Summer Research \textit{Internship} Program \hspace*{1.5mm} --- IIT - Gandhinagar $||$ $<$ 0.008\% Selection rate. $||$ 2023 Cohort
\\
UKRI Fast Start: Innovation \textit{Grant} \hspace*{5.5mm} --- Co-Applicant $||$ $\sim$ \pounds50000 $||$ 2022 Cohort \\
MITACS Globalink Research \textit{Internship} --- TRIUMF (UVic) $||$ $<$ 3\% Selection rate $||$ 2021 Cohort
\\

SPIE Medical Imaging'25 \hspace{0.55cm} --- Travel Grant Award $||$ \$1000 \\

IEEE ISBI'24  \hspace{2.25cm} --- Best Student Poster Award Finalist. (Top 8 out 717 Acceptances)

IEEE ICETCI'21 \textit{Competition}  --- 3$^{rd}$ Place (Electronic Substation Detection)

\vspace{-3mm}

%-----------Graduate Teaching------------
\section{Graduate Teaching}
\vspace{-1mm}
Journal Club -- Biomedical Enggineering $|$ Winter 24 \& Spring 25 {\scriptsize(Short Course)} \hfill{} Prof. Monica Agromayor\\
Statistics \hspace{0.56cm}-- Biomedical Enggineering 
 $|$ Spring 25 {\scriptsize(Short Course)} \hfill{} Prof.  James Housden\\

\end{document}
