%-------------------------
% Resume in Latex
% Author : Soumya Kundu
% License : MIT
%------------------------
\documentclass[letterpaper,10pt]{article}

% Imports
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{multicol}
\usepackage{contour}
\usepackage{ulem}
\usepackage{xcolor}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage{enumitem}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.9in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-----------------------------
% Custom commands
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}

% Underline
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}
%-----------------------------

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large \scshape Soumya Snigdha Kundu} \\ [0.2cm]

    \small +44-7436-215-187 $|$
    \href{https://www.linkedin.com/in/soumyaskundu/}
    {\myuline{Linkedin}}  $|$
    \href{https://scholar.google.com/citations?user=WmHtKBYAAAAJ&hl=en&oi=ao}
    {\myuline{G-Scholar}} $|$
    \href{https://github.com/aymuos15}
    {\myuline{Github}} $|$
    \href{https://aymuos15.github.io/}
    {\myuline{Website}} $|$
    \href{https://discuss.pytorch.org/u/soumya_kundu/summary}
    {\myuline{PyTorch-Forums}} $|$
    \href{mailto:soumyawork15@gmail.com} 
    {\myuline{E-mail}} $|$ 
    London, United Kingdom
\end{center}


%----------EDUCATION----------
\textcolor{blue}{\textbf{\myuline{EDUCATION}}} \\[0.2cm]

\textbf{King's College London} \\
\textit{PhD} in Biomedical Engineering and Imaging Science Research  \\
Advisors: Prof. Tom Vercauteren and Dr. Jonathan Shapey \\
Thesis Committee: Dr. Jorge Cardoso, Dr. Marc Modat and Prof. Andrew Reader\\
Thesis: Artificial Intelligence-driven Management of Brain Tumours \\[0.2cm]

\textbf{Queen Mary University of London} \\
\textit{MSc (Distinction)} in Machine Learning in Visual Data Analytics  \\
Advisors: Prof. Greg Slabaugh and Dr. Vineet Batta \\
Thesis: Unveiling the Localization Advantage in Automated Orthopaedic Implant Identification \\[0.2cm]

\textbf{SRM Institute of Science and Technology} \\
\textit{B.Tech (Distinction)} in Computer Science and Engineering (Minor: Cloud Computing)  \\
Advisor: Prof. Dhanalakshmi Samiappan \\
Thesis: On the Feasibility of Neural Network Pruning in Covid-19 Classification. \\[0.4cm]


%----------Research EXPERIENCE----------
\textcolor{blue}{\textbf{\myuline{RESEARCH EXPERIENCE}}} \\ [0.2cm]

\textbf{University of Oxford} | Prof. Bartek Papiez \\ [0.1cm]
$[$Fall 2023] Research Intern \\ [0.1cm]
Project: Pilot work on Spinal Osteophyte Identification \\ [0.2cm]

\textbf{IIT-Gandhinagar}  | Prof. Tarun Gangwar \\ [0.1cm]
$[$Summer 2023] Research Intern \\ [0.1cm]
Project: Image to Simulation (Im2Sim) Software workflow for Patient-specific fully Autonomous Diagnostic Simulations \\[0.2cm]

\textbf{NepAl Applied Mathematics and Informatics Institute for research} (NAAMII) | Prof. Bishesh Khanal \\ [0.1cm]
$[$Summer 2022] Research Intern \\ [0.1cm]
Project: Explainability in Automated Orthopaedic Implant Identification \\[0.2cm]

\textbf{TRIUMF: Canada's particle accelerator centre}  | Prof. Akira Konaka and Dr. Patrick De Perio \\ [0.1cm]
$[$Fall 2021] Research Intern \\ [0.1cm]
Project: Development of Advanced Deep Learning Methods for Neutrino Interaction Event Reconstruction in Hyper-Kamiokande Water Cherenkov Detectors \\[0.2cm]

\textbf{NIT-Durgapur} | Prof. Debashis Nandi \\ [0.1cm]
$[$Spring \& Summer 2021] Research Intern \\ [0.1cm]
Project: Multi-Modal Brain Lesion Segmentation \\[0.2cm]

\textbf{National Chung Cheng University} | Prof. Pao-Ann Hsiung \\ [0.1cm]
$[$Fall 2020] Research Intern \\ [0.1cm]
Project: Automated Face-Mask Detection \\ [0.2cm]

\textbf{Indian Statistical Institute} | Prof. Bidyut Baran Chaudhuri \\ [0.1cm]
$[$Summer 2020] Research Intern \\ [0.1cm]
Project: Exploring Compound Normalisation techniques in Convolutional Neural Networks. \\[0.2cm]

\textbf{College of Engineering, Guindy} | Prof. Saswathi Mukherjee \\ [0.1cm]
$[$Winter 2019] Research Intern \\ [0.1cm]
Project: Application of Machine Learning Tools and Techniques in Healthcare \\[0.4cm]


%----------Industry EXPERIENCE----------
\textcolor{blue}{\textbf{\myuline{INDUSTRY EXPERIENCE}}} \\ [0.2cm]

\textbf{IIIT-Hyderbad \& TCS Research} | Prof. Ranjitha Prasad and Mrs. Ramya Hebbalaguppe \\ [0.1cm]
$[$Summer 2024] Research Associate \\ [0.1cm]
Project: Trustworthy Out of Domain Machine Learning\\ [0.2cm]

\textbf{Stealth Startup} \\
$[$Jan 2022- Sept 2023] Founding Engineer \\
Project: Pilot deployment of Automated Orthopaedic Implant Identification \\[0.2cm]


%----------PUBLICATIONS----------
\textcolor{blue}{\textbf{\myuline{PUBLICATIONS}}} \\[0.2cm]
\bibliographystyle{IEEEtran}
\nobibliography{pubs}

\textbf{Journals} \\
\begin{enumerate}
\setlength{\itemsep}{0pt} % Remove vertical space between items
\item \bibentry{kumar2022lightweight}
\item \bibentry{vineth2022radiological}
\end{enumerate}

\textbf{Conferences} \\
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item \bibentry{kundu2024spinal} \\
\item \bibentry{mishra2023harnessing} \\
\item \bibentry{kundu2021distributed} \\
\item \bibentry{bhalla2021automatic} \\
\item \bibentry{sreenivasan2021machine}
\end{enumerate}

\textbf{Posters/Workshops} \\
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item \textbf{S. S. Kundu}, A. Kujawa, M Ivory, T. Barfoot, J.
Shapey, and T. Vercauteren, "Cluster Dice: A simple and fast approach for instance based semantic segmentation evaluation via many-to-many matching", \myuline{SPIE: Medical Imaging} 2025.
\item \textbf{S. S. Kundu} and P. Ganesh, "Promptly-Cited: Citation based Prompting via Pseudo-Retrieval-Augmented Generation", in \myuline{Women in Machine Learning Workshop @ Conference on Neural Information Processing Systems} (NeurIPS), 2024.
\item R. Naidu and \textbf{S. S. Kundu}, "Improved variants of Score-CAM via Smoothing and Integrating", \myuline{Responsible Computer Vision Workshop @ Conference on Computer Vision and Pattern Recognition} (CVPR), 2021. 
\end{enumerate}

\textbf{Clinical - Posters} \\
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item \textbf{S. S. Kundu}, S. Patel, A. Ramanathan, D. Chonko, A. Kurmis, and V. Batta, "Data constrained deep learning to improve scenarios in revision arthroplasty where preoperative identification of the make and model of the primary (in-situ) implant is critical", in 2023 \myuline{IEEE International Symposium on Biomedical Imaging} (ISBI).
\item  \textbf{S. S. Kundu}., Kartik M. V., Paul Y., S. Kaminei, C. Malathy, S. Patil, Ravi P., D. Elson and Batta V,
"Automated identification of orthopaedic implants on radiographs using AI", \myuline{AI in Orthopaedics Confernece}, 2022. 
\item \textbf{S. S. Kundu}, S. Baldota, G. Mani, M. Chidambaranathan, K. Mohan, M. Prabhakaran, R. Takad,
B. Datta, S. Kamineni, G. Reddy, S. Masilamani A. B, S. Vijayan, D. Amantullah, and V. Batta, "Analysis of Anteroposterior and Lateral views in Total Hip Arthroplasty Implant Identification.", \myuline{66$^{th}$ Annual Conference of Indian Orthopaedic Association}, 2021.
\item S. Baldota, \textbf{S. S. Kundu}, S. Sharma, V. Batta, M. Kiruthika, M. Chidambaranathan, G. Mani,
Prabhakaran M., R. Takad, B. Datta, S. Kamineni, G. Reddy, S. Masilamini, S. Vijayan, and D. Amanatulla., "Automated Recognition of Total Hip Arthroplasty Implants", 41$^{st}$ \myuline{SICOT Orthopaedic World Congress}, 2021.
\end{enumerate}

\textbf{Reviewing} \\ [0.1cm]
Conferences: ICLR, NeurIPS, and IEEE ISBI. \\
Workshops: ICML-ML4LMS, MICCAI-CaPTion, NeurIPS-WiML and MICCAI-FAIMI. \\ [0.4cm]

\textbf{Talks}
\begin{enumerate}
    \item "Exploring Instance Imbalance in Medical Semantic Segmentation" for Voxel 51
\end{enumerate}

%----------ACHIEVEMENTS----------
\textcolor{blue}{\textbf{\myuline{ACHEIVEMENTS}}} \\[0.2cm]
\textbf{Scholarships} \\ [0.1cm]
MRC DTP Postgraduate \textit{Studentship} \hspace*{2.8mm} --- King's College London $||$ 2023 Cohort $||$ $<$ 2\% Selection rate  \\ [0.1cm]
BDI Summer \textit{Internship} Programme \hspace*{4mm} --- University of Oxford $||$ 2023 Cohort $||$ 1 of 4 selected applicants \\ [0.1cm]
Summer Research \textit{Internship} Program \hspace*{1.5mm} --- IIT - Gandhinagar $||$ 2023 Cohort $||$ $<$ 0.008\% Selection rate. \\ [0.1cm]
MITACS Globalink Research \textit{Internship} --- TRIUMF (UVic) $||$ 2021 Cohort $||$ $<$ 3\% Selection rate \\ [0.2cm]

\textbf{Grants} \\ [0.1cm]
UKRI Fast Start: Innovation \textit{Grant} \hspace*{5.5mm} --- Co-Applicant $||$ 2022 Cohort $||$ $\sim$ \pounds50000 \\ [0.2cm]

\textbf{Coding/Conference Competitions} \\ [0.1cm]
IEEE ISBI'24 \hspace*{2.45cm} --- Best Student Poster Award Finalist. (Top 8 out 717 Acceptances) \\ [0.1cm]

Anthropic Hackathon London --- Top 8 Finalist \\ [0.1cm]

IEEE ICETCI'21 \textit{Competition}  --- 3$^{rd}$ Place (Electronic Substation Detection) \\ [0.4cm]


%----------PROGRAMMING----------
\textcolor{blue}{\textbf{\myuline{PROGRAMMING}}} \\[0.2cm]
Languages (Primary): Python, C++, Bash, Git. \\ [0.1cm]
Libraries: PyTorch, JAX, NumPy, OpenCV, pandas, \LaTeX \\ [0.1cm]
Softwares: CUDA, Docker, Github, SLURM. \\ [0.1cm]
Languages (Secondary): HTML, CSS, JavaScript. \\ [0.4cm]
% Operating System: Linux, Windows, Macintosh. \\ [0.4cm]

%----------Summer School----------
\textcolor{blue}{\textbf{\myuline{SUMMER SCHOOLS}}} \\[0.2cm]
2024 Summer Workshop on Surgical and Interventional Engineering \\ [0.1cm]
2023 Oxford Machine Learning Summer School (Healthcare Track) 
\\ [0.1cm]
2022 Intelligent Sensing Winter School \\ [0.1cm]
2021 ACM Europe Summer School on HPC Computer Architectures for AI and Dedicated Applications
\\ [0.1cm]
2021 5th Summer School on AI With focus on Computer Vision \& Machine Learning \\ [0.4cm]

%----------SUPERVISION---------
\textcolor{blue}{\textbf{\myuline{SUPERVISION}}} \\[0.2cm]
[Fall 2024] Aarav Kannar - M.B.B.S Student at University of Lancanshire \\ [0.4cm]


%----------VOLUNTEER----------
\textcolor{blue}{\textbf{\myuline{VOLUNTEERING}}} \\ [0.2cm] 
National Medical Research Council Doctoral Training Programme (MRC DTP) Representative \\ [0.1cm]
Host - In2Stem Programme \\ [0.4cm]


%----------References----------
\textcolor{blue}{\textbf{\myuline{REFERENCES}}} \\ [0.2cm]

\begin{tabular}
{p{0.5\textwidth} p{0.5\textwidth}}
\textbf{Prof. Tom Vercauteren} & \textbf{Mr. Jonathan Shapey} \\
Professor of Interventional Image Computing & Clinical Reader in Neurosurgery \\
King's College London & King's College London and King's College Hospital \\
Advisor (Ph.D.) & Advisor (Ph.D.)
\end{tabular}

\vspace{2mm}

\begin{tabular}
{p{0.5\textwidth} p{0.5\textwidth}}
\textbf{Prof. Greg Slabaugh} & \textbf{Mr. Vineet Batta} \\
Professor of Computer Vision and AI & Senior Clinical Fellow Trauma \& Orthopaedics \\
Queen Mary University of London & Luton and Dunstable University Hospital \\
Advisor (MSc) & Advisor (MSc)
\end{tabular}

\vspace{2mm}

\begin{tabular}
{p{0.5\textwidth} p{0.5\textwidth}}
\textbf{Prof. Bartek Papiez} \\
Associate Professor \\
Unversity of Oxford \\
Mentor \\ [0.4cm]
\end{tabular}


%----------EXTRA-CURRICULARS----------
\textcolor{blue}{\textbf{\myuline{EXTRA-CURRICULARS}}} \\ [0.2cm]
Team India --- Futsal (2017) \\ [0.1cm]
Team Tamil Nadu --- Futsal (2016) (Nationals Silver Medal)  \\ [0.1cm]
Middle/High School Football Team Captain [2014-17] 


\end{document}